A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-06-12 ms.tex
All citations work. Partway through updating text.

%\documentclass[10pt,iop]{emulateapj}
\documentclass[preprint]{aastex}
%\usepackage{rotating}
\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
%\usepackage{graphicx}
%\usepackage[figuresright]{rotating}
%\usepackage{rotating}
%%\usepackage{natbib}

@@

\newcommand{\Nconf}{31}
\newcommand{\Nsrc}{32}

@@

\begin{abstract}
We present a catalog of broad-band spectral measurements from the 
Donald C. Backer Precision Array for Probing
the Epoch of Reionization (PAPER) in South Africa observed in July and
September of 2011.  In order to reduce the impact of beam calibration, which proves to
be a difficult endeavor for transit telescopes such as PAPER, on the determination
of source spectra, we have focused on calibrating sources in a narrow declination range.
Since each source follows a nearly identical path through the primary beam, this
restriction allows beam calibration to be greatly reduced as a source of error,
yielding a dramatic improvement in the accuracy of source spectra measured in the 
100--200-MHz band which is receiving renewed attention by experiments seeking to
measure 21cm emission from the Epoch of Reionization (EoR). Using beam forming
and fringe-rate filtering we measure spectra for Pictor A, which provides a key flux reference for PAPER's EoR
power spectrum analysis, 
as well as \Nconf other sources at nearby declinations. Extrapolating from higher frequency
catalogs we set the flux scale in a monte-carlo fit across multiple sources. This fit 
propagates uncertainty from both catalog and measurement errors. Fitting new spectral 
models to both catalog and the new PAPER data we find a Pictor A flux model accurate to
2.4\%.
This accuracy is limited by the uncertainty in the catalog measurements we use
to estimate an absolute flux scale, and represents 
an order of magnitude improvement over previous measurements in this band.  
Comparing with prior measurements, 90\% are found to confirm and refine a power-law model for flux density.

@@

Numerous radio telescopes are now exploring the prospects for using
measurements of highly redshifted 21cm emission to inform our understanding of
cosmic reionization in the redshift range $6< z<12$, corresponding to radio
frequencies below 200 MHz (see reviews in
\citealt{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}).  These
include telescopes aiming to measure the global temperature change of 21cm
emission during the Epoch of Reionization (EoR), such as the Compact
Reionization Experiment (CoRE) and the Experiment to Detect the Global EoR
Signature (EDGES; \citealt{Bowman:2010p8546}), and interferometers aiming to
measure the power spectrum of 21-cm EoR emission, such as the Giant Metre-wave
Radio Telescope (GMRT;
\citealt{Paciga:2011p9470,Paciga:2013p9627})\footnote{\url{http://gmrt.ncra.tifr.res.in/}},
the LOw Frequency ARray (LOFAR;
\citealt{Yatawatta:2013p9699})\footnote{\url{http://www.lofar.org/}}, the
Murchison Widefield Array (MWA;  \citealt{Bowman:2012p9138};
\citealt{Tingay:2013p9022}))\footnote{\url{http://www.mwatelescope.org/}}, and
the Donald C. Backer Precision Array for Probing the Epoch of Reionization
(PAPER; \citealt{Parsons:2010p6757,Parsons2013b})\footnote{\url{http://eor.berkeley.edu/}}.

As such, there has been a renewed interest in the spectral and spatial variation of
foreground emission in the 100--200 MHz frequency band that covers
the $z=6$--13 redshift range expected to encompass reionization
\citep{furlanetto_et_al2006}.
In particular, the spectral properties of extra-galactic point-sources are important
both because they are valuable calibration references
and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
With the sparse availability of measured foreground properties in the
100--200-MHz frequency band over large areas of the sky \citep{deolivieracosta_et_al2008}, continued
foreground characterization is a
vital step en route to any 21-cm EoR detection.
At these low
frequencies the Southern sky is much less well known than the North, 
with catalog source fluxes at 150MHz being inaccurate at the 20\% level
for $\delta<-20$\arcdeg (XXX cite).
Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
reserves being prepared for the upcoming Square Kilometer Array, and hence,
the
most extensive surveying work is now being conducted by the EoR experiments
themselves \citep{Jacobs:2011p8438,Williams:2012p8768,Bernardi:2013p9859}.

One significant complication to improving the state of affairs in foreground characterization
is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
PAPER and MWA in the southern hemisphere, are designed for drift-scan observations.
This design decision has largely been driven by the simplicity and cost-effectiveness of
phased and/or correlated dipoles for achieving the aggressive sensitivity requirements
for measuring the 21cm power spectrum of reionization (XXX cite).
Adding to the challenge, these telescopes 
cover much wider fields of view ($>10$\arcdeg) and bandwidths
($\sim 100$\% fractional) than traditional dish telescopes.
Because they do not physically point, flux calibration for such arrays relies heavily
on an accurate model of the primary beam response to correct for an
the apparent flux scale that varies across the sky.
This direction dependent gain is currently uncertain to 10\% or higher
% XXX 20% seems a bit grim.  Doesn't jonnie argue for 5 to 10% in his paper?
%XXX 20\% comes from the overall uncertainty between MWA and PAPER, part of which is also side lobes. 
%	Jonnie's fluxes are dominated by the side lobes in the pgb16 data, the fluxes have a range of errors around 15 to 20%
\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9713}.

In this paper, we set out to significantly improve the accuracy of spectral measurements between 
100--200 MHz for a set of bright sources in the declination range -46\arcdeg to -40\arcdeg that
are of particular value for southern-hemisphere 21cm EoR experiments such as PAPER and the MWA.
Using the fact that, for this restricted declination range,
sources transit through a nearly identical primary beam response pattern, we are able to avoid one of the
most debilitating source of error in these measurements: the primary beam.  
% XXX update document map
In \S\ref{sec:analysis} we describe our approach for measuring source spectra with
drift-scan observations and deriving an absolute flux scale from catalog data.  
In \S\ref{sec:Observations} we detail the instrumental 
setup, observations and analysis method followed. In \S\ref{sec:fits} we
compare the spectra with available data.  We conclude in 
\S\ref{sec:Conclusion}.

@@

\section{Background}

% XXX unsure about this section.  need someplace to give overviews of catalogs

@@

%0518-458	 PKS, Pictor A	G	 25.93	 24.01	1		W	 0.0342	 23.63	 176.
% XXX transition to the PAPER instrument
Establishing an accurate spectrum for Pictor A is of particular importance for
PAPER --- a dedicated EoR experiment 
that employs drift-scanning, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band.  PAPER is located in the South African Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
The PAPER array has grown from 16 elements deployed in early 2009 to a
64-element imaging array in 2011 (see Figure \ref{fig:antpos}). 
Since November 2011 it has been arranged in a maximally redundant grid 
configuration to make deep power spectral integrations \citep{Parsons:2012a}.
Though highly sensitive as a power spectrum instrument, the maximally redundant array 
has a broad point spread function in the image domain. This severely limits the number 
of sources which may be used for flux calibration. Drift scanning across the sky with a 45\arcdeg FWHM
primary beam there are very few unresolved, bright sources which are far from the galactic plane. 
Pictor A is bright and well enough separated from other emission to dominate the visibilities for a good fraction of
the EoR observing season, making it an ideal flux calibrator.

@@

\subsection*{Data Processing Overview}
\label{sec:data_overview}
The spectra reported here are measured by beam-forming ---phasing the visibilities to
the target location and summing to produce a dynamic spectrum. The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time average is 
weighted by an additional factor of PAPER's primary beam response 
\citep{pober_et_al2012}.  
\begin{align}
S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M} \nonumber \\ 
&= \frac{\sum_t B_M B}{\sum_t B^2_M} S  \nonumber \\
&= g(\delta) S  \label{eq:g}
\end{align}

which is an effective approximation of inverse-variance weighting. The pre factor in Eq \ref{eq:g} is identical for 
sources at the same declination.  In simulation we multiplied an early attempt to map the beam \cite{Pober:2012p8800}
by electromagnetic simulations of the PAPER beam and find that it 
diverges slowly with declination, with a maximum of 10\% over 5\arcdeg of declination range.
We estimate this spectral dependent gain at a reference declination of 41\arcdeg36\arcmin using (J2331-416) fitting a spectral index model to the
 well-defined data points below 2GHz.

 Finally we average the spectra from a resolution of 400kHz to 10MHz bins, taking the standard deviation within these bins
 for an estimate of the uncertainty.

At this point we have a set of spectra that have been calibrated relative to each other to the best of our ability. Now 
they must be put on a global flux scale. We also have only a limited estimate of our error from our intra-channel
rms.  To address both points we fit for a global flux scale that incorporates data from many catalogs. These catalogs
have all been set, as best as possible, to the Baars et al scale.  Using a Bayesian analysis we compute the 
variation in the flux scale implied by comparing many sources to prior catalog. By including sources from across
the declination range,the variation in this flux scale fit estimates the overall uncertainty in flux resulting from primary beam 
or prior catalog uncertainty.  So though the final scale is calibrated to the Baars scale as extrapolated beyond its
defined band, the error on the flux scale fully encapsulates the error resulting from this extrapolation.

@@

In pre-processing, we use delay/delay-rate (DDR) filters
\citep{Parsons:2009p7859} to identify radio-frequency interference (RFI)
events, and as part of a data compression technique that reduces data volume by
over a factor of 40.  A more detailed description may be found in Appendix A of
\cite{Parsons2013b}, which uses the same compression method on PAPER power
spectrum observations. Here we summarize the process.

@@

% XXX merge with below
%Removed RFI by flagging samples in each frequency channel versus time that exceed the mean amplitude by 4-sigma
%after performing a time derivative.  Also flagged samples in each integrated spectrum that exceeded the
%mean amplitude across the spectrum by 6-sigma after performing a frequency derivative.  For efficiency, flagging
%was derived using only the subset of baselines involving a fiducial antenna.
%Frequencies below 120 MHz and above 180 MHz were also flagged, owing to roll-off of analog response.
%After RFI flagging, frequency channel resolution was decreased by a factor of four by summing channels.

%I'm Confused.  These are describing a different ordering of steps. Must re-read compression script.

@@

Small gain variations between antennae and over time introduce significant systematic effects which degrade 
instrument performance. Temporal variations are dominated by changes in ambient temperature. 
Measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
are known to exhibit.  A predicted gain profile was derived using coefficients characterized in
laboratory measurements \citep{parashare_bradley2009} and
confirmed in field measurements \citep{pober_et_al2011} of $H_{\rm balun}=-0.024$ dB/K, $H_{\rm recvr}=-0.045$
dB/K, and $H_{\rm cable}=-0.018$ dB/K for 150m-long cables.  Because cable temperatures were not measured
during these observations, the cable temperature was assumed to be the same as the measured balun temperature.

Matching of relative gains and phases between antenna was done by fitting a per-antenna complex gain to portions
of data which have easily modeled sky. 
This calibration is only relative between antennae, absolute flux calibration
comes after time and frequency averaging in  \S \ref{sec:flux_scale}.   
The antenna delays and amplitudes were found by fitting a point source visibility
model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
modeled by a single point-source, but the solution differences are minimized by
averaging over the three independent solutions. These same calibration
solutions have been successfully applied in \citet{Pober:2013XXX} and \citet{Stefan:2013:XXX}.
for power-spectrum analysis of foregrounds and imaging of Centaurus A, respectively.

@@

The resulting set of spectra were then calibrated to a model of J2331-416 to remove 
the residual bandpass due to the net effect of the primary beam as discussed in \S \ref{sec:approach}. J2331-416 
\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$} fit to measurements beolow 1GHz \citep{slee1995,kuhr_et_al1981,large_et_al1981,burgess_hunstead2006}.
was selected for its relatively high brightness, spectral smoothness and large quantity
 of available catalog data. Each source track has a slightly different sample profile
 resulting from different amounts of flagged data at each time and channel. To account
 for these differences in the bandpass calibration we build a set of calibration tracks 
 that match the tracks for each source. Calibration of each source then proceeds with
 an optimally matched calibration spectrum.

@@

\subsection{Fitting a Power-Law Model to Spectra}

@@

Here we use the emcee sampler by \citet{Mackay:2003p9717} et al to generate chains of
parameter values. The best fit model is the median of all the sampled
parameter sets, while the volume containing a well defined fraction of samples
sets the confidence limits.  The oft quoted ``1$\sigma$" probability level
corresponding to a gaussian distribution contains 65\% of the samples. In
practice the contours are not gaussian. Here we choose a slightly more
conservative probability level of 76\%

@@

Confidence contours for
the complete set are shown in grey in Figs. \ref{fig:SI_contour_1} -
\ref{fig:SI_contour_4}.  In general these are lower limits on the possible
precision, as the Vollmer catalog emphasizes minimization of cross-match error
but at the cost of excluding data points.  The fit is then performed again with
both PAPER and catalog data, shown in black on the same Figures. The values are
given in Table \ref{tab:fits}, and
illustrated in Figure \ref{fig:src_spec}.

@@

\section{Results and Discussion}
\label{sec:fits}
%TODO Revise all the numbers in this session.
%now we have 32 sources (counting pic)
% 25 have >0 improvement
% 0 have negative
% 6 have 0 overlap
In the 59 sources measured, four demonstrated poor convergence fitting a single
spectral index to both the PAPER data and prior catalog data. In three
cases\footnote{1243-412,1247-401,1315-460} %TODO update these sources are in
the Centaurus A/galactic plane region. Though the beam forming method provides
relatively high dynamic range of $\sim$100:1 it is unable to distinguish
between these sources and the bright diffuse Centaurus and galactic structure.
The last source, 0008-421, was not detected by previous PAPER observations and
exhibits flattening at higher frequencies, most likely due to synchrotron
self-absorption \citep{Jacobs:2011p8438} .  The remaining 94\% MCMC chains
arrived at a stable posterior distribution. The spectral index parameters for
these chains are given in table \ref{tab:fits}.

Inspecting the confidence contours we find that, for the vast majority ($\sim
75$\%), the PAPER measurements confirm the power law extrapolation from higher
frequencies. The remaining 25\% either A) have large PAPER error bars and
therefore provide no new information or B) do not agree with the spectral index
model.  To understand where most measurements fall on this spectrum we
numerically quantify the overall model improvement derived from the addition of
the PAPER data as 
\begin{align}
\textrm{Improvement} &= \left(\textrm{Precision increase}\right) \left(\textrm{Catalog agreement}\right)\\
&= \left(\frac{1}{\textrm{Area}(\textrm{PAPER})} - \frac{1}{\textrm{Area}(\textrm{Cat})}\right) \left( \textrm{Area}(\PAPER \cap \textrm{Cat}) \right)
\end{align}
where the area is defined as the number of samples having posterior probability above 76\%.

We quantify the fit {\em precision increase} as the change in the contour
figure of merit, defined as the inverse area of the confidence contour.
Meanwhile, {\em catalog agreement} is the fraction of the PAPER confidence
interval that overlaps the catalog confidence interval.  Thus, for example, in
a PAPER fit that overlaps the catalog confidence contour by 41\% but increases
in precision (confidence area shrinks) by a factor of 3, the resulting {\em
improvement} will be 0.123.

In these sources, the improvement index ranges from a max of 6.9 to -0.022.
10\% of sources showed negative improvement, suggesting that PAPER data have
added to uncertainty (see Figure \ref{fig:SI_contour_bad}). 12\% of sources
have exactly zero improvement, which indicates that the PAPER data have pulled
the fit far from the model preferred by the catalog data (see Fig.
\ref{fig:SI_contour_new}).  The spectral models of these sources have not been
included in Table \ref{tab:fits}.  The remainder of the spectral fits are
included for completeness, but given the range of quality found, particularly
near the Galactic plane and Centaurus A, should be used with utmost caution.

However, the majority of source 78\% have positive improvement index,
indicating strong confirmation of the extrapolated spectrum (see Figures
\ref{fig:SI_contour_1} - \ref{fig:SI_contour_4}).  Pictor A is in the middle of
this group  with an improvement of 0.39 ---only 14 sources show stronger
confirmation.  The flux model is $S150=$388 $\pm$ 9.4Jy, $\alpha=-0.77\pm0.02$.
The combination of several independent PAPER data points near 150MHz with
previous catalog measurements results in this estimated uncertainty of 2.4\%.
This uncertainty is dominated by agreement between the 2 Wills measurements
near 600MHz which are accurate to 2\% and the five PAPER measurements, which
are accurate to ~5\%.  This error estimate includes an estimate of accuracy of the overall flux scale,
as well as the source-source variation due to primary beam errors.

@@

\end{center}
\caption{
These fits are somehow at odds with other measurements.  The 1526-42 spectrum is visibly curved (see Fig. \ref{fig:srcs1), which explains the large disagreement in spectral index but not flux. 1424-418 is an optically polarized quasar with a flat and variable radio spectrum which might imply co-aligned jet viewing and high intrinsic variability. 
} \label{fig:SI_contour_new}
\end{figure*}

>>>>

%\documentclass[10pt,iop]{emulateapj}
\documentclass[preprint]{aastex}
%\usepackage{rotating}
\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{xcolor}
%\usepackage{graphicx}
%\usepackage[figuresright]{rotating}
%\usepackage{rotating}
%%\usepackage{natbib}

@@

\newcommand{\Nconf}{31}
\newcommand{\Nsrc}{32}
\definecolor{orange}{RGB}{255,127,0}

@@

\begin{abstract}
We present a catalog of broad-band spectral measurements from the 
Donald C. Backer Precision Array for Probing
the Epoch of Reionization (PAPER) in South Africa observed in July and
September of 2011.  In order to reduce the impact of beam calibration, which proves to
be a difficult endeavor for transit telescopes such as PAPER, on the determination
of source spectra, we have focused on calibrating sources in a narrow declination range.
Since each source follows a nearly identical path through the primary beam, this
restriction allows beam calibration to be greatly reduced as a source of error,
yielding a dramatic improvement in the accuracy of source spectra measured in the 
100--200-MHz band which is receiving renewed attention by experiments seeking to
measure 21cm emission from the Epoch of Reionization (EoR). Using beam forming
and fringe-rate filtering we measure spectra for Pictor A, which provides a key flux reference for PAPER's EoR
power spectrum analysis, 
as well as \Nconf other sources at nearby declinations. Extrapolating from higher frequency
catalogs we set the flux scale in a Monte-C`arlo fit across multiple sources. This fit 
propagates uncertainty from both catalog and measurement errors. Fitting new spectral 
models to both catalog and the new PAPER data we find a Pictor A flux model accurate to
2.4\%.
This accuracy is limited by the uncertainty in the catalog measurements we use
to estimate an absolute flux scale, and represents 
an order of magnitude improvement over previous measurements in this band.  
Comparing with prior measurements, 90\% are found to confirm and refine a power-law model for flux density.

@@

Numerous radio telescopes are now exploring the prospects for using
measurements of highly redshifted 21cm emission to inform our understanding of
cosmic reionization in the redshift range $6< z<12$, corresponding to radio
frequencies below 200 MHz (see reviews in
\citealt{Furlanetto:2006p2267,Morales:2010p8093,Pritchard:2012p9555}).  These
include telescopes aiming to measure the global temperature change of 21cm
emission during the Epoch of Reionization (EoR), such as the Compact
Reionization Experiment (CoRE), the Zero-spacing Interferometer \citep{Raghunathan:2011}  and the Experiment to Detect the Global EoR
Signature (EDGES; \citealt{Bowman:2010p8546}), and interferometers aiming to
measure the power spectrum of 21-cm EoR emission, such as the Giant Metre-wave
Radio Telescope (GMRT;
\citealt{Paciga:2011p9470,Paciga:2013p9627})\footnote{\url{http://gmrt.ncra.tifr.res.in/}},
the LOw Frequency ARray (LOFAR;
\citealt{Yatawatta:2013p9699})\footnote{\url{http://www.lofar.org/}}, the
Murchison Widefield Array (MWA;  \citealt{Bowman:2012p9138};
\citealt{Tingay:2013p9022}))\footnote{\url{http://www.mwatelescope.org/}}, and
the Donald C. Backer Precision Array for Probing the Epoch of Reionization
(PAPER; \citealt{Parsons:2010p6757,Pober:2013p9567})\footnote{\url{http://eor.berkeley.edu/}}.

As such, there has been a renewed interest in the spectral and spatial variation of
foreground emission in the 100--200 MHz frequency band that covers
the $z=6$--13 redshift range expected to encompass reionization
\citep{Furlanetto:2006p2267}.
In particular, the spectral properties of extra-galactic point-sources are important
both because they are valuable calibration references
and because they are strong foreground emitters that must be removed from 21-cm EoR measurements.
With the sparse availability of measured foreground properties in the
100--200-MHz frequency band over large areas of the sky \citep{deOliveiraCosta:2008p2242}, continued
foreground characterization is a
vital step en route to any 21-cm EoR detection.
At these low
frequencies the Southern sky is much less well known than the North, 
with catalog source fluxes at 150MHz being inaccurate at the 20\% level
for $\delta<-20$\arcdeg \citep{Slee:1995p7541,Vollmer:2005p6425}.
Both PAPER and the MWA are located in the southern hemisphere at radio-quiet
reserves being prepared for the upcoming Square Kilometer Array, and hence,
the
most extensive surveying work is now being conducted by the EoR experiments
themselves \citep{Jacobs:2011p8438,Williams:2012p8768,Bernardi:2013p9859}.

One significant complication to improving the state of affairs in foreground characterization
is that many 21cm EoR experiments, including LOFAR in the northern hemisphere, and
PAPER and MWA in the southern hemisphere, are designed for drift-scan observations or steered via phased array.
This design decision has largely been driven by the simplicity and cost-effectiveness of
phased and/or correlated dipoles to achieve the aggressive sensitivity requirements
for measuring the 21cm power spectrum of reionization.
%TODO ARP wanted a cite for the above.  I really don't know of a good one. Its it a bit of a broad statement
Adding to the challenge, these telescopes 
cover much wider fields of view ($>10$\arcdeg) and bandwidths
($\sim 100$\% fractional) than traditional dish telescopes.
Because they do not physically point, flux calibration for such arrays relies heavily
on an accurate model of the primary beam response to correct for an
the apparent flux scale that varies across the sky.
This direction dependent gain is currently uncertain to 10\% or higher
\citep{Pober:2012p8800}, and comprises a large fraction of the 20\% difference between current telescopes \citep{Jacobs:2013p9713}.

In this paper, we set out to significantly improve the accuracy of spectral measurements between 
100--200 MHz for a set of bright sources in the declination range -46\arcdeg to -40\arcdeg that
are of particular value for southern-hemisphere 21cm EoR experiments such as PAPER and the MWA.
Using the fact that, for this restricted declination range,
sources transit through a nearly identical primary beam response pattern, we are able to avoid one of the
most debilitating source of error in these measurements: the primary beam.  
% XXX update document map
In section \ref{sec:background} we provide some background on uncertainty in early EoR-band catalogs,
and explain our choice of calibrator. Section \ref{sec:approach} gives an overview 
of our approach to making the measurement and motivates our data processing steps, which 
are described in detail in section \ref{sec:Observations}. In section

In section \ref{sec:approach} we describe our approach for measuring source spectra with
drift-scan observations and deriving an absolute flux scale from catalog data.  
In \S\ref{sec:Observations} we detail the instrumental 
setup, observations and analysis method followed. Sections \ref{sec:mcmc} through
\ref{fig:gain} detail our approach for fitting a global flux scale and spectral models for each source.
We use these fits in section \ref{sec:results} to understand how well PAPER data agree
with previous measurements and conclude in \ref{sec:Conclusion}.

@@

\section{Background}
\label{sec:background}
% XXX unsure about this section.  need someplace to give overviews of catalogs

@@

%0518-458	 PKS, Pictor A	G	 25.93	 24.01	1		W	 0.0342	 23.63	 176.
% XXX transition to the PAPER instrument
Establishing an accurate spectrum for Pictor A is of particular importance for
PAPER --- a dedicated EoR experiment 
that employs drift-scanning, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band.  PAPER is located in the South African Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
The PAPER array has grown from 16 elements deployed in early 2009 to a
64-element imaging array in 2011 (see Figure \ref{fig:antpos}). 
Since November 2011 it has been arranged in a maximally redundant grid 
configuration to make deep power spectral integrations \citep{Parsons:2012p9028}.
Though highly sensitive as a power spectrum instrument, the maximally redundant array 
has a broad point spread function in the image domain. This severely limits the number 
of sources which may be used for flux calibration. Drift scanning across the sky with a 45\arcdeg FWHM
primary beam there are very few unresolved, bright sources which are far from the galactic plane. 
Pictor A is bright and well enough separated from other emission to dominate the visibilities for a good fraction of
the EoR observing season, making it an ideal flux calibrator.

@@

\subsection*{Data Processing Overview}
\label{sec:data_overview}
The spectra reported here are measured by beam-forming ---phasing the visibilities to
the target location and summing to produce a dynamic spectrum. The spectrum is then isolated
from neighboring sources by filtering and averaged in the time domain.  This time average is 
weighted by an additional factor of PAPER's primary beam response 
\citep{Pober:2012p8800}.  
\begin{align}
S_\textrm{est} &= \frac{\sum_t B_M S_p}{\sum_t B^2_M} \nonumber \\ 
&= \frac{\sum_t B_M B}{\sum_t B^2_M} S  \nonumber \\
&= g(\delta) S  \label{eq:g}
\end{align}

which is an effective approximation of inverse-variance weighting. The pre factor in Eq \ref{eq:g} is identical for 
sources at the same declination.  In simulation we multiplied an early holographic beam map \cite{Pober:2012p8800}
by electromagnetic simulations and find that it 
diverges slowly with declination, with a maximum of 10\% over 5\arcdeg of declination range.
We estimate this spectral dependent gain at a reference declination of 41\arcdeg36\arcmin using (J2331-416) fitting a spectral index model to the
 well-defined data points below 2GHz.

 Finally we average the spectra from a resolution of 400kHz to 10MHz bins, adding the individual errors in quadrature
 as our uncertainty.

At this point we have a set of spectra that have been calibrated relative to each other to the best of our ability. Now 
they must be put on a global flux scale. Meanwhile, our error estimate does not include an estimate of the 
flux calibration error.  To address both points we fit for a global flux scale that incorporates data from many catalogs. These catalogs
have all been set, as best as possible, to the Baars et al scale.  Using a Bayesian analysis we compute the 
variation in the flux scale implied by comparing many sources to prior catalog models. By including sources from across
the declination range,the variation in this flux scale fit estimates the overall uncertainty in flux resulting from primary beam 
or prior catalog uncertainty.  Though the final scale is calibrated to the Baars scale, as extrapolated beyond its
lower limit of 300 MHz, the flux scale error derived by this method fully describes the error resulting from this extrapolation.

@@

In pre-processing, we use delay/delay-rate (DDR) filters
\citep{Parsons:2009p7859} to identify radio-frequency interference (RFI)
events, and as part of a data compression technique that reduces data volume by
over a factor of 40.  A more detailed description may be found in Appendix A of
\cite{Parsons:2013p9876}, which uses the same compression method on PAPER power
spectrum observations. Here we summarize the process.

@@

@@

Small gain variations between antennae and over time introduce significant systematic effects which degrade 
instrument performance. Temporal variations are dominated by changes in ambient temperature. 
Measurements of ambient temperature versus time near the balun amplifier of a fiducial antenna and near
receiver amplifiers were used to divide out the predicted gain variation versus temperature that these amplifiers
are known to exhibit.  Inspecting the auto correlations we find that the net temperature gain coefficient (-0.042 dB/C) found in previous laboratory \cite{Parashare:2011p9872} and early field 
measurements  \cite{Pober:2012p8800} did not appear to remove all temperature variation (black curve in Figure \ref{fig:auto_compare}).  To
revise the temperature coefficient we use the October observations, when the temperatures remained nearly constant, as a reference.

Comparing the average ratio between the July and October autocorrelations to their temperature difference (Figure \ref{fig:autos_tempcorr}) we find that the two are highly correlated  with 
a best fit temperature coefficient of (-0.058 dB/C). As we see in the Figure \ref{fig:auto_compare}, this removes a significant amount of disagreement between the two nights, 
with the peak difference decreasing from 18\% to 3\%.
\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/auto_tempcorr.png}
\caption{Calibrating the temperature coefficient by comparing the two nights.  Here we plot the ratio of auto-correlations (averaged over frequency and antenna) against the temperature difference between the two data sets. The very linear middle region has a slope of  -0.055 dB/C while the full, more complex, range is fit by -0.06dB/C (black line).  We compromise by choosing -0.058dB/C.   \label{fig:autos_tempcorr}}
\end{figure}
\begin{figure}
\includegraphics[width=0.9\textwidth]{plots/auto_balance.png}
\caption{Gain differences between the July and October nights are dominated by temperature variation. Here we see the affect on 
the average auto correlation before ({\color{orange} orange}) and after (black) application of the temperature dependent gain. \label{fig:auto_compare}}
\end{figure}

Matching of relative gains and phases between antenna was done by fitting a per-antenna complex gain to portions
of data which have easily modeled sky. 
This calibration is only relative between antennae, absolute flux calibration
comes after time and frequency averaging in  \S \ref{sec:flux_scale}.   
The antenna delays and amplitudes were found by fitting a point source visibility
model to Centaurus A, Pictor A, and Fornax A.  Each source is imperfectly
modeled by a single point-source, but the solution differences are minimized by
averaging over the three independent solutions. These same calibration
solutions have been successfully applied in \citet{Pober:2013p9567} and \citet{Stefan:2012p9707}.
for power-spectrum analysis of foregrounds and imaging of Centaurus A, respectively.

@@

The resulting set of spectra were then calibrated to a model of J2331-416 to remove 
the residual bandpass due to the net effect of the primary beam as discussed in \S \ref{sec:approach}. J2331-416 
\footnote{Here we set the spectrum to $S_{150}=33$Jy, $\alpha=-0.76$} a somewhat arbitrary 
fit to measurements below 1GHz \citep{Slee:1995p7541,Kuehr:1981p9628,Large:1981p7798,Burgess:2006p7814}.
was selected for its relatively high brightness, spectral smoothness and large quantity
 of available catalog data. Each source track has a slightly different sample profile
 resulting from different amounts of flagged data at each time and channel. To account
 for these differences in the bandpass calibration we build a set of calibration tracks 
 that match the tracks for each source. Calibration of each source then proceeds with
 an optimally matched calibration spectrum.

@@

\subsection{Fitting a Power-Law Model to Spectra}
\label{sec:mcmc}

@@

Here we use the \emph{emcee} sampler by \citet{Mackay:2003p9717} et al to generate chains of
parameter values. The best fit model is the median of all the sampled
parameter sets, while the volume containing a well defined fraction of samples
sets the confidence limits.  The oft quoted ``1$\sigma$" probability level
corresponding to a gaussian distribution contains 65\% of the samples. In
practice the contours are not gaussian. Here we choose a slightly more
conservative probability level of 76\%

@@

Confidence contours for
the complete set are shown in grey in Figs. \ref{fig:SI_contour_1} -
\ref{fig:SI_contour_2}.  In general these are lower limits on the possible
precision, as the Vollmer catalog emphasizes minimization of cross-match error
but at the cost of excluding data points.  The fit is then performed again with
both PAPER and catalog data, shown in black on the same Figures. The values are
given in Table \ref{tab:fits}, and
illustrated in Figure \ref{fig:src_spec}.

@@

\section{Results and Discussion}
\label{sec:results}
%TODO Revise all the numbers in this session.
%now we have 32 sources (counting pic)
%%>0 improvement: 27
%%<0 improvement: 1
%%=0 improvement: 3
%total 31
The majority of the \Nsrc models fit using the new PAPER data were found to agree with
models fit to past data and all but two are suitable for comparison.  
0008-421 was not detected by previous PAPER observations and
exhibits flattening at higher frequencies, most likely due to synchrotron
self-absorption \citep{Jacobs:2011p8438}. While 1459-417 does not have enough 
measurements in the Vollmet et al catalog on which to build a model for comparison. We exclude these 
two from further analysis.

Inspecting the remaining 29 confidence contours we find that, for the vast majority ($\sim
90$\%), the PAPER measurements confirm the power law extrapolation from higher
frequencies. The remaining 10\% either A) have large PAPER error bars and
therefore provide no new information or B) do not agree with the spectral index
model.  To understand where most measurements fall on this spectrum we
numerically quantify the overall model improvement derived from the addition of
the PAPER data as 
\begin{align}
\textrm{Improvement} &= \left(\textrm{Precision increase}\right) \left(\textrm{Catalog agreement}\right)\\
&= \left(\frac{1}{\textrm{Area}(\textrm{PAPER})} - \frac{1}{\textrm{Area}(\textrm{Cat})}\right) \left( \textrm{Area}(\PAPER \cap \textrm{Cat}) \right)
\end{align}
where the area is defined as the number of samples having posterior probability above 76\%.

We quantify the fit {\em precision increase} as the change in the contour
figure of merit, defined as the inverse area of the confidence contour.
Meanwhile, {\em catalog agreement} is the fraction of the PAPER confidence
interval that overlaps the catalog confidence interval.  Thus, for example, in
a PAPER fit that overlaps the catalog confidence contour by 41\% but increases
in precision (confidence area shrinks) by a factor of 3, the resulting {\em
improvement} will be 0.123.  This Improvement Index is included in the table
of fit parameters (Table \ref{tab:fits}).

In these sources, the improvement index ranges from a maximum of 7.84  to -0.001.
One source (1017-421) shows a slightly negative improvement, suggesting that PAPER data have
added to uncertainty (see Figure \ref{fig:SI_contour_bad}), while two sources
have exactly zero improvement, which indicates that the PAPER data have pulled
the fit far from the model preferred by the catalog data (see Fig.
\ref{fig:SI_contour_new}).

However, the vast majority of sources (90\%) have positive improvement index,
indicating strong confirmation of the extrapolated spectrum (see Figures
\ref{fig:SI_contour_1} - \ref{fig:SI_contour_3}).  Pictor A is in the middle of
this group  with an improvement of 0.942 ---only two sources show stronger
confirmation.  The flux model is $S150=$381 $\pm$ 5.36Jy, $\alpha=-0.76\pm0.01$.
The combination of several independent PAPER data points near 150MHz with
previous catalog measurements results in this estimated uncertainty of 1.4\%.
This uncertainty is quite small, but is not surprising when we consider that we have
used 7 precise data points (5 PAPER, 2 Wills), all accurate to 3\% to measure what appears to
be an extremely linear power law spectrum. If the errors were completely guassian
the net error would be $3/\sqrt(7) = 1.14$\%.

@@

\end{center}
\caption{
These fits are somehow at odds with other measurements.  The 1526-42 spectrum is visibly curved (see Fig. \ref{fig:srcs1}), which explains the large disagreement in spectral index but not flux. 1424-418 is an optically polarized quasar with a flat and variable radio spectrum which might imply co-aligned jet viewing and high intrinsic variability. 
} \label{fig:SI_contour_new}
\end{figure*}
